---
title: "Offsite Trial Reporting"
author: "Matt McLean"
date: "13/05/2020"
output:
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis', warning=FALSE, message=FALSE)
#install.packages('bcmapsdata', repos='https://bcgov.github.io/drat/')
library(bcdata)
library(bcmaps)
library(bcmapsdata)
library(matrixStats)
library(tidyverse)
library(knitr)
library(kableExtra)
library(sf)
library(flextable)
library(spData)
library(mapview)
library(tmap)
library(ggplot2)
library(ggthemes)
library(ape)
library(leaflet)
library(lubridate)
source("functions/plot_summary.R")
source("functions/climate_summary.R")

```
<!--- Configuration --->
```{r}
load(here::here("trial_data.Rdata"))
seedlots = all_data$seedlots
trees = all_data$trees
climate = all_data$climate
plots = all_data$plots
meta = all_data$meta
sites = distinct(select(merge(meta, plots, by="FID"), Location, FID, Lat, Lon), Location, FID, .keep_all = TRUE) #Location based on a plot not center of entire site
climate_sites = distinct(climate, ClimateStationID)
#List of years for which tree data is present, don't try to plot dates outside this range
years = year(as.character(min(as.date(as.character(trees$Date))))):year(as.character(max(as.date(as.character(trees$Date)))))
#List of years for climate data can differ from plot data.
climate_years = year(as.character(min(as.date(as.character(climate$Date))))):year(as.character(max(as.date(as.character(climate$Date)))))

#This function was used by many of the plots, moved here to not repeat
tree_summary=list()
for(year in years){
  tree_summary[[year]] <- trees %>% 
    filter(year(as.character(Date)) == year) %>%
    # need to convert seedlot to factor
    mutate(Seedlot=factor(Seedlot)) %>% 
    
    # Relevel condition factors
    mutate(Condition=fct_relevel(Condition,"Missing","Dead", "Moribund","Poor","Fair","Good")) %>% # reorder levels
    
    # Create plot summaries
    group_by(FID,Plot,Species,Seedlot,Condition) %>% 
    summarise(n=n()) %>% # summarize number of trees at FID/Plot/Species/Condition
    ungroup()
}

#Define custom colour scheme, though we are using theme_few() which has defualt colour ramps, they make our plots look like easter egges, Rules 3, 4, 7
#TODO: Reduce contrast in palette Rule 5
condition_colours = c(Missing='black', Dead='red', Moribund='orange', Poor='yellow', Fair='green', Good='darkgreen','purple') #Purple is missing data, if you see this color in charts there is incomplete records for trees 
frost_stats = temperature_events(climate, 0)
hard_frost_stats = temperature_events(climate, -4)

```
# Study Information
## Map
```{r}
points <- st_as_sf(x = sites %>% mutate(FID), coords = c("Lon", "Lat"), crs = "+proj=longlat")
center = st_coordinates(points$geometry) %>% matrix(ncol=2,byrow=FALSE)
#TODO: Prevent Labels overlapping, increase bounding box size
mapview(points["FID"], legend = FALSE, map.types = c("OpenTopoMap"), labelOptions=leaflet::labelOptions(noHide=TRUE), clusterOptions=leaflet::markerClusterOptions())
```

## Seedlots
```{r}
lot_table = as.data.frame(t(seedlots %>% select(Seedlot, Species, Code, Provenance = Provenance.description, Lat, Long, Elevation, 'Mean annual temperature (째C)' = MAT, "Mean wamest month temperature (째C)" = MWMT, "Mean coldest month temperature (째C)" = MCMT, "Number of frost free days" = NFFD, "Continious frost-free period (days)" = FFP, "Mean annual precipitation (mm" = MAP, "Mean summer precipitation (mm)" = MSP, "Precipitation as snow (mm)" = PAS)))
colnames(lot_table) = as.character(unlist(lot_table[1,]))
kable(lot_table[-1, ]) %>% kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% column_spec(1:ncol(lot_table)+1, border_left = T, width = "7em") %>% column_spec(1, width = "10em")
```

# Graphical Comparisons

## Seedling condition by species{.tabset}
```{r}
for(year in years){
  cat("  \n### ", year, "  \n")
  print(tree_summary[[year]] %>% 
          group_by(Species, Condition) %>% 
          summarise(Condition.Mean=mean(n)) %>% 
          
          mutate(Condition.Percent = Condition.Mean/sum(Condition.Mean)) %>%
          
          # Plotting
          ggplot()+
          aes(x=Species,y=Condition.Percent,fill=Condition)+
          geom_bar(stat="Identity")+
          theme_few() + scale_fill_manual(values = alpha(condition_colours, .8)))
  cat("  \n")
}
```

## Seedling condition by trial {.tabset}
```{r}
for(year in years){
  cat("  \n### ", year, "  \n")
  print(tree_summary[[year]] %>% 
          group_by(FID, Condition) %>% 
          summarise(Condition.Mean=mean(n)) %>% 
          
          mutate(Condition.Percent = Condition.Mean/sum(Condition.Mean)) %>%
          
          # Plotting
          ggplot()+
          aes(x=FID,y=Condition.Percent,fill=Condition)+
          geom_bar(stat="Identity")+
          theme_few() + theme(axis.text.x = element_text(angle = 90))+
          scale_fill_manual(values = alpha(condition_colours, .8)))
  cat("  \n")
}
```

## Seedling condition by trial and species {.tabset}
```{r fig.height=10}
for(year in years){
  cat("  \n### ", year, "  \n")
  print(tree_summary[[year]] %>% 
          group_by(Species,FID,Condition) %>% 
          summarise(Condition.Mean=mean(n)) %>% 
          
          mutate(Condition.Percent = Condition.Mean/sum(Condition.Mean)) %>%
          
          # Plotting
          ggplot()+
          aes(x=Species,y=Condition.Percent,fill=Condition)+
          geom_bar(stat="Identity")+
          facet_wrap(~FID,ncol=3,scales="free_x")+
          theme_few() + theme(axis.text.x = element_text(angle = 90))+ scale_fill_manual(values = alpha(condition_colours, .8)))
  cat("  \n")
}
```

## Seedling condition by seedlot {.tabset}
```{r}
for(year in years){
  cat("  \n### ", year, "  \n")
  print(tree_summary[[year]] %>% 
          group_by(Species,Seedlot,Condition) %>% 
          summarise(Condition.Mean=mean(n)) %>% 
          
          mutate(Condition.Percent = Condition.Mean/sum(Condition.Mean)) %>%
          
          # Plotting
          ggplot()+
          aes(x=Seedlot,y=Condition.Percent,fill=Condition)+
          geom_bar(stat="Identity")+
          facet_wrap(~Species,ncol=3,scales="free_x")+
          theme_few() + theme(axis.text.x = element_text(angle = 90)) + scale_fill_manual(values = alpha(condition_colours, .8)))
  cat("  \n")
}
```

## Mean of condition class for each species {.tabset}
```{r}
for(year in years){
  cat("  \n### ", year, "  \n")
  print(tree_summary[[year]] %>% 
          group_by(Species,Condition) %>% 
          summarise(Condition.Mean=mean(n), Condition.stdev=sd(n), Condition.count = n())%>% 
          
          mutate(Condition.Percent = Condition.Mean/sum(Condition.Mean)) %>%
          mutate(Condition.stdev.p = Condition.stdev/sum(Condition.Mean)) %>%
          mutate(Condition.sterror = Condition.stdev/sqrt(Condition.count)) %>%
          mutate(Condition.sterror.p = Condition.sterror/sum(Condition.Mean)) %>%
          # Plotting
          ggplot()+
          aes(x=Condition,y=Condition.Percent)+
          geom_bar(stat="Identity")+
          facet_wrap(~Species,ncol=3,scales="free_x")+
          theme_few() + theme(axis.text.x = element_text(angle = 90)) + scale_fill_manual(values = alpha(condition_colours, .8)) +
          geom_errorbar( aes(x=Condition, ymin=Condition.Percent-Condition.sterror.p, ymax=Condition.Percent+Condition.sterror.p), width=0.4, colour="orange", alpha=0.9, size=1))
  cat("  \n")
}
```

## Height by Species
```{r}
trees %>% group_by(Species, year=year(Date)) %>% filter(!is.na(Height)) %>% summarize(mean_height = mean(Height, na.rm=TRUE)) %>% ggplot() + aes(x=year, y=mean_height, color=Species) + geom_line(stat="Identity")
```

## Height by Seedlot
```{r}
trees %>% group_by(Seedlot, year=year(Date)) %>% filter(!is.na(Height)) %>% summarize(mean_height = mean(Height, na.rm=TRUE)) %>% ggplot() + aes(x=year, y=mean_height, color=Seedlot) + geom_line(stat="Identity")
```

## Height by FID
```{r}
trees %>% group_by(FID, year=year(Date)) %>% filter(!is.na(Height)) %>% summarize(mean_height = mean(Height, na.rm=TRUE)) %>% ggplot() + aes(x=year, y=mean_height, color=FID) + geom_line(stat="Identity")
```


## Diameter by Species
```{r}
trees %>% group_by(Species, year=year(Date)) %>% filter(!is.na(Height)) %>% summarize(mean_diam = mean(Diameter, na.rm=TRUE)) %>% ggplot() + aes(x=year, y=mean_diam, color=Species) + geom_line(stat="Identity")
```


## Diameter by Seedlot
```{r}
trees %>% group_by(Seedlot, year=year(Date)) %>% filter(!is.na(Height)) %>% summarize(mean_diam = mean(Diameter, na.rm=TRUE)) %>% ggplot() + aes(x=year, y=mean_diam, color=Seedlot) + geom_line(stat="Identity")
```

## Diameter by FID
```{r}
trees %>% group_by(FID, year=year(Date)) %>% filter(!is.na(Height)) %>% summarize(mean_diam = mean(Diameter, na.rm=TRUE)) %>% ggplot() + aes(x=year, y=mean_diam, color=FID) + geom_line(stat="Identity")
```

## Temperature

### Overview {.tabset}
```{r}
#Frost stats overview loops though climate stations making one tab for each, multiple sites and years on single graph is too messy.
for(site in climate_sites[[1]]){
  cat("   \n####", as.character(site), "   \n")
  #ggplot with 3 layers first is minimum dayly temperature, then hard frost events as solid dimonds, finally frost events as X's. Plot is grouped by years, where each year get's it's own colour.
  print(ggplot() + 
          geom_line(data = climate %>% mutate(day = lubridate::yday(Date), year = year(Date)) %>% group_by(year, day, ClimateStationID) %>% filter(ClimateVar == "temp" & ClimateStationID == as.character(site)) %>% summarise(minimum_daily_temp = min(Value)), stat="Identity", aes(x=as.numeric(day), y=minimum_daily_temp, color=year), alpha=.5)  + 
          geom_point(data = hard_frost_stats[[site]], stat="Identity", aes(x=lubridate::yday(Date), y=0 - as.numeric(as.character(hard_frost_stats[[site]]$Magnitude)), fill=year(Date)), colour = 'black', shape=23, size=2, show.legend = F)) + 
          geom_point(data = frost_stats[[site]], stat="Identity", aes(x=lubridate::yday(Date), y=0 - as.numeric(as.character(frost_stats[[site]]$Magnitude)), color=year(Date)), shape=4, size = 2, show.legend = F) + theme_few() + labs(y="Minimum Temperature (째C)", x = "Day of Year")
  cat("   \n")
}
```

### Events Below Theshold {.tabset}
```{r}
for(year in climate_years){
  cat("  \n#### ", year, "  \n")
  
  print(ggplot(data = temperature_summary(climate, 0, -4, paste(year, "-01-01", sep=""),paste(year, "-12-31", sep=""))  %>% arrange(ClimateStationID) %>% select(ClimateStationID, num_frost_events, num_hard_frost_events) %>% gather(Threshold, num_events, -ClimateStationID), aes(x = ClimateStationID, y = as.numeric(num_events), fill = Threshold)) + geom_bar(stat = 'identity', position = 'dodge') + theme_few() + theme(axis.title.y=element_blank(), axis.text.x = element_text(angle = 90)) + ggtitle("Number of events below threshold"))
}
```

### Maximum Magnitude {.tabset}
```{r}
for(year in climate_years){
  cat("  \n#### ", year, "  \n")
  #magnitude must be cast to character before numeric or conversion issues arrive
  print(ggplot(data=temperature_summary(climate, 0, -4, paste(year, "-01-01", sep=""),paste(year, "-12-31", sep=""))  %>% arrange(ClimateStationID), aes(x=ClimateStationID, y=as.numeric(as.character(max_magnitude)))) + geom_bar(stat="identity") + theme_few() + theme(axis.title.y=element_blank(), axis.text.x = element_text(angle = 90)) + ggtitle("Maximum Magnitude at ClimateStationID"))
}
```

### Total Hours Below Threshold {.tabset}
```{r}
for(year in climate_years){
  cat("  \n#### ", year, "  \n")
  
  print(ggplot(data = temperature_summary(climate, 0, -4, paste(year, "-01-01", sep=""),paste(year, "-12-31", sep=""))  %>% arrange(ClimateStationID) %>% select(ClimateStationID, frost_duration, hard_frost_duration) %>% gather(Threshold, duration, -ClimateStationID), aes(x = ClimateStationID, y = as.numeric(duration), fill = Threshold)) + geom_bar(stat = 'identity', position = 'dodge') + theme_few() + theme(axis.title.y=element_blank(), axis.text.x = element_text(angle = 90)) + ggtitle("Hours Below Threshold"))
}
```

# Statistical Comparisons

## Growth(Height) by FID
```{r}
#Checks for correlation between sites over years, high correlation suggests that speific trial site does not affect growth
height_by_FID = pivot_wider(trees %>% group_by(FID, year=year(Date)) %>% summarize(mean_height = mean(Height, na.rm=TRUE)), names_from = year, values_from = mean_height)
growth_by_FID = height_by_FID[1]
for (year in 2:(ncol(height_by_FID)-1)){
  growth_by_FID[year] = cbind(height_by_FID[year + 1] - height_by_FID[year])
}
print(kable(growth_by_FID)%>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Standard Deviation\n")
print(kable(rbind(colnames(growth_by_FID[,2:ncol(growth_by_FID)]), colSds(as.matrix(growth_by_FID[,2:ncol(growth_by_FID)]), na.rm=TRUE))) %>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Correlation\n")
print(kable(cor(growth_by_FID[2:ncol(growth_by_FID)], use="complete.obs")) %>% kable_styling(bootstrap_options = c("striped", "hover")))

```

## Growth(Diameter) by FID
```{r}
#Checks for correlation between sites over years, high correlation suggests that speific trial site does not affect growth
diameter_by_FID = pivot_wider(trees %>% group_by(FID, year=year(Date)) %>% summarize(mean_diameter = mean(Diameter, na.rm=TRUE)), names_from = year, values_from = mean_diameter)
growth_by_FID = diameter_by_FID[1]
for (year in 2:(ncol(diameter_by_FID)-1)){
  growth_by_FID[year] = cbind(diameter_by_FID[year + 1] - diameter_by_FID[year])
}
print(kable(growth_by_FID)%>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Standard Deviation\n")
print(kable(rbind(colnames(growth_by_FID[,2:ncol(growth_by_FID)]), colSds(as.matrix(growth_by_FID[,2:ncol(growth_by_FID)]), na.rm=TRUE))) %>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Correlation\n")
print(kable(cor(growth_by_FID[2:ncol(growth_by_FID)], use="complete.obs")) %>% kable_styling(bootstrap_options = c("striped", "hover")))

```

## Growth(Height) by Species
```{r}
#Mean Growth by Species
height_by_Species = pivot_wider(trees %>% group_by(Species, year=year(Date)) %>% summarize(mean_height = mean(Height, na.rm=TRUE)), names_from = year, values_from = mean_height)
growth_by_Species = height_by_Species[1]
for (year in 2:(ncol(height_by_Species)-1)){
  growth_by_Species[year] = cbind(height_by_Species[year + 1] - height_by_Species[year])
}
print(kable(growth_by_Species)%>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Standard Deviation\n")
print(kable(rbind(colnames(growth_by_Species[,2:ncol(growth_by_Species)]), colSds(as.matrix(growth_by_Species[,2:ncol(growth_by_Species)]), na.rm=TRUE))) %>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Correlation\n")
#Checks for correlation between sites over years
print(kable(cor(growth_by_Species[2:ncol(growth_by_Species)], use="complete.obs")) %>% kable_styling(bootstrap_options = c("striped", "hover")))

```

## Growth(Diameter) by Species
```{r}
#Mean Growth by Species
diameter_by_Species = pivot_wider(trees %>% group_by(Species, year=year(Date)) %>% summarize(mean_diameter = mean(Diameter, na.rm=TRUE)), names_from = year, values_from = mean_diameter)
growth_by_Species = diameter_by_Species[1]
for (year in 2:(ncol(diameter_by_Species)-1)){
  growth_by_Species[year] = cbind(diameter_by_Species[year + 1] - diameter_by_Species[year])
}
print(kable(growth_by_Species)%>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Standard Deviation\n")
print(kable(rbind(colnames(growth_by_Species[,2:ncol(growth_by_Species)]), colSds(as.matrix(growth_by_Species[,2:ncol(growth_by_Species)]), na.rm=TRUE))) %>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Correlation\n")
#Checks for correlation between sites over years
print(kable(cor(growth_by_Species[2:ncol(growth_by_Species)], use="complete.obs")) %>% kable_styling(bootstrap_options = c("striped", "hover")))

```

## Growth(Height) by Seedlot
```{r}
#Mean Growth by Seedlot
height_by_Seedlot = pivot_wider(trees %>% group_by(Seedlot, year=year(Date)) %>% summarize(mean_height = mean(Height, na.rm=TRUE)), names_from = year, values_from = mean_height)
growth_by_Seedlot = height_by_Seedlot[1]
for (year in 2:(ncol(height_by_Seedlot)-1)){
  growth_by_Seedlot[year] = cbind(height_by_Seedlot[year + 1] - height_by_Seedlot[year])
}
print(kable(growth_by_Seedlot)%>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Standard Deviation\n")
print(kable(rbind(colnames(growth_by_Seedlot[,2:ncol(growth_by_Seedlot)]), colSds(as.matrix(growth_by_Seedlot[,2:ncol(growth_by_Seedlot)]), na.rm=TRUE))) %>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Correlation\n")
#Checks for correlation between sites over years, high correlation suggests lower influence of seed providence
print(kable(cor(growth_by_Seedlot[2:ncol(growth_by_Seedlot)], use="complete.obs")) %>% kable_styling(bootstrap_options = c("striped", "hover")))
```

## Growth(Diameter) by Seedlot
```{r}
#Mean Growth by Seedlot
diameter_by_Seedlot = pivot_wider(trees %>% group_by(Seedlot, year=year(Date)) %>% summarize(mean_diameter = mean(Diameter, na.rm=TRUE)), names_from = year, values_from = mean_diameter)
growth_by_Seedlot = diameter_by_Seedlot[1]
for (year in 2:(ncol(diameter_by_Seedlot)-1)){
  growth_by_Seedlot[year] = cbind(diameter_by_Seedlot[year + 1] - diameter_by_Seedlot[year])
}
print(kable(growth_by_Seedlot)%>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Standard Deviation\n")
print(kable(rbind(colnames(growth_by_Seedlot[,2:ncol(growth_by_Seedlot)]), colSds(as.matrix(growth_by_Seedlot[,2:ncol(growth_by_Seedlot)]), na.rm=TRUE))) %>% kable_styling(bootstrap_options = c("striped", "hover")))

cat("   \n### Correlation\n")
#Checks for correlation between sites over years, high correlation suggests lower influence of seed providence
print(kable(cor(growth_by_Seedlot[2:ncol(growth_by_Seedlot)], use="complete.obs")) %>% kable_styling(bootstrap_options = c("striped", "hover")))
```

## Spatial Correllation
```{r}

fids = as.data.frame(trees %>% distinct(FID) )
for(id in 1:nrow(fids)) {
  feature <- as.vector(fids$FID[[id]])
  cat("  \n####",  feature, "  \n")
  tree_list = as.data.frame(trees %>% filter(FID == feature & (Lon != 0 | Lat != 0)))
  if (nrow(tree_list) > 0){
    tree_distance = as.matrix(dist(cbind(tree_list$Lat, tree_list$Lon)))
    inverse_tree_distance = 1/tree_distance
    tree_list %>% mutate(Condition=fct_relevel(Condition,"Missing","Dead", "Moribund","Poor","Fair","Good"))
    inverse_tree_distance[is.infinite(inverse_tree_distance)] <- 0
    moran = Moran.I(as.numeric(tree_list$Condition), inverse_tree_distance)
    cat("  \nObserved: ", moran$observed)
    cat("  \nExpected: ", moran$expected)
    cat("  \nStandard Deviation: ", moran$sd)
    cat("  \np-value: ", moran$p, "  \n---------------------------")
    #TODO what correleation is considered clustered for this data set?
    if(moran$p > 0.5){
      cat("  \nNot Statistically Significant!")
    }
    if(moran$observed - .1 > moran$expected){
      cat("  \nClustered Distribution")
    }
    else if(moran$observed + .1 < moran$expected){
      cat("  \nDispursed Distribution")
    }
    else{
      cat("  \nRandom Distribution")
    }
  }
  else{
    cat("   \nTree positions unknown")
  }
  cat("  \n")
}
```

## Temperature
```{r}
#Graphs are printed for each year
#TODO: Are seasons dates correct?
for (year in year(as.character(min(as.date(as.character(climate$Date))))):year(as.character(max(as.date(as.character(climate$Date)))))){
  cat("  \n### ", year)
  cat("   \n#### Entire Growing Seasion")
  print(kable(temperature_summary(climate, 0, -4, paste(year, '01-01', sep='-'), paste(year, '12-31', sep='-'))  %>% arrange(ClimateStationID)))
  cat("   \n#### Early Spring")
  print(kable(temperature_summary(climate, 0, -4, paste(year, '01-01', sep='-'), paste(year, '05-31', sep='-'))  %>% arrange(ClimateStationID)))
  cat("   \n#### Summer")
  print(kable(temperature_summary(climate, 0, -4, paste(year, '06-01', sep='-'), paste(year, '08-31', sep='-'))  %>% arrange(ClimateStationID)))
  cat("   \n#### Atumn")
  print(kable(temperature_summary(climate, 0, -4, paste(year, '09-01', sep='-'), paste(year, '12-31', sep='-'))  %>% arrange(ClimateStationID)))
}

```

# Appendix

## Data Tables

### Plot Summaries
```{r}

fids = as.data.frame(trees %>% distinct(FID))
for(id in 1:nrow(fids)) {
  feature <- as.vector(fids$FID[[id]])
  cat("  \n####",  feature, "  \n")
  print(kable(plot_summary(filter(trees, FID == feature))))
}
```

### Treatment Summaries
```{r}
treatments = as.data.frame(trees %>% distinct(Species, Seedlot))
print(kable(treatment_summary(trees)))
cat("  \n###")
```
### Treatments by Species
```{r}
treatments = as.data.frame(trees %>% distinct(Species))
print(kable(species_summary(trees)))
cat("  \n####")
```
### Treatments by Seedlot
```{r}
treatments = as.data.frame(trees %>% distinct(Seedlot))
print(kable(seedlot_summary(trees)))
cat("  \n####")
```

## Seedlot by Species
```{r}
Species = as.data.frame(trees %>% distinct(Species))
for(id in 1:nrow(Species)) {
  feature <- as.vector(Species$Species[[id]])
  cat("  \n####",  feature, "  \n")
  print(kable(seedlot_by_species(feature, trees)))
}
```

## Condition by Trial
```{r}
ss = as.data.frame(trees %>% distinct(Species, Seedlot))
for(id in 1:nrow(ss)) {
  feature <- as.vector(c(ss$Seedlot[[id]], as.character(ss$Species[[id]])))
  cat("  \n####",  feature, "  \n")
  print(kable(condition_by_trial(feature, trees)))
}

```

## Height by Species
```{r}
print(kable(pivot_wider(trees %>% group_by(Species, year=year(Date)) %>% summarize(mean_height = mean(Height, na.rm=TRUE)), names_from = year, values_from = mean_height)))
```


## Height by Seedlot
```{r}
print(kable(pivot_wider(trees %>% group_by(Seedlot, year=year(Date)) %>% summarize(mean_height = mean(Height, na.rm=TRUE)), names_from = year, values_from = mean_height)))
```

## Height by FID
```{r}
print(kable(pivot_wider(trees %>% group_by(FID, year=year(Date)) %>% summarize(mean_height = mean(Height, na.rm=TRUE)), names_from = year, values_from = mean_height)))
```


## Diameter by Species
```{r}
print(kable(pivot_wider(trees %>% group_by(Species, year=year(Date)) %>% summarize(mean_diam = mean(Diameter, na.rm=TRUE)), names_from = year, values_from = mean_diam)))
```


## Diameter by Seedlot
```{r}
print(kable(pivot_wider(trees %>% group_by(Seedlot, year=year(Date)) %>% summarize(mean_diam = mean(Diameter, na.rm=TRUE)), names_from = year, values_from = mean_diam)))
```

## Diameter by FID
```{r}
print(kable(pivot_wider(trees %>% group_by(FID, year=year(Date)) %>% summarize(mean_diam = mean(Diameter, na.rm=TRUE)), names_from = year, values_from = mean_diam)))
```

### Temperature
```{r}
for(table in 1:length(frost_stats)){
  cat("   \n#### Frost", names(frost_stats[table]))
  print(kable(frost_stats[[table]]))
  cat("   \n#### Hard Frost", names(hard_frost_stats[table]))
  print(kable(hard_frost_stats[[table]]))
}
```

## Site Maps
```{r}
#tmap_mode("view") #Interactive view mode not currently support by R-Markdown
for (site in sites$FID){
  points <- st_as_sf(x = all_data$trees %>% filter(FID == site) %>% mutate(Condition=fct_relevel(Condition,"Good","Fair", "Poor", "Moribund","Dead", "Missing")), coords = c("Lat", "Lon"), crs = "+proj=longlat")
  map = tm_shape(points["Condition"]) + tm_view(set.zoom.limits = c(18,24)) + tm_dots(size =0.75, col="Condition", palette=c(Good='green', Fair='yellow', Poor='orange', Moribund='red', Dead='black', Missing='blue', 'purple')) + tm_layout(site, legend.outside=TRUE, legend.title.size=1, legend.text.size = 0.6)
  cat("  \n###",  site, "  \n")
  print(map)
  cat("  \n")
  #mapview(points["Condition"], col.regions = c("Missing" = "Black", "Moribund" = "Red", "Poor" = "Orange", "Fair" =  "Yellow", "Good" = "Green"), lwd = 0, cex = 5)
}

```




