---
title: "Preliminary analysis of 2020 data"
author: "Hardy Griesbauer"
date: "10/02/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning=FALSE,
                      fig.width=8,
                      fig.height=8)

# Libraries
library(tidyverse)

# Load data
load(here::here("data/2020_data","data2020.RData"))

```

## Seedling condition

Let's explore seedling condition (as of Fall 2020) by species, seedlot and site type:

```{r seedling condition summaries}

data2020 %>% 
  filter(!Type %in% c("Demo")) %>% # remove frost and demo sites
  drop_na(Condition_2020fa) %>% # there are a few trees with no condition recorded in Fall 2020 (see e-mail from Brett)
  group_by(Type,Species,Distance,Condition_2020fa) %>% 
  summarise(n=n()) %>% 
  mutate(freq = n / sum(n)) %>% # remember one grouping level peeled off with each summarise
  
  ggplot()+
  aes(x=Condition_2020fa,y=freq,fill=Distance)+
  geom_bar(stat="identity",position="dodge")+
  facet_grid(Species~Type)+
  xlab("Condition fall 2020")+
  ylab("Proportion")+
  labs(fill="Seed dist.")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2, hjust=1))





```

- Notice how few novel trees are in good/fair condition on the frost site, especially compared to Pli and Sx.
- Notice that the novel tree species seem to be in better condition on the dry site.

\newpage

We can show seedling condition a little differently.  The figure below allows to compare seedling condition between seedlot, by site type.

```{r seedling condition summaries 2nd way}

data2020 %>% 
  filter(!Type %in% c("Demo")) %>% # remove frost and demo sites
  drop_na(Condition_2020fa) %>% # there are a few trees with no condition recorded in Fall 2020 (see e-mail from Brett)
  group_by(Type,Species,Distance,Condition_2020fa) %>% 
  summarise(n=n()) %>% 
  mutate(freq = n / sum(n)) %>% # remember one grouping level peeled off with each summarise
  
  ggplot()+
  aes(x=Distance,y=freq,fill=Condition_2020fa)+
  geom_bar(stat="identity",position="stack")+
  facet_grid(Species~Type)+
  xlab("Seedlot distance")+
  ylab("Proportion")+
  labs(fill="Seedling condition")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2, hjust=1))





```

\newpage

Another way of looking at the same data.  Here, seedling condition is arranged to allow comparison of site type, within seedlot:

```{r seedling condition summaries 3rd way}


data2020 %>% 
  filter(!Type %in% c("Demo")) %>% # remove frost and demo sites
  drop_na(Condition_2020fa) %>% # there are a few trees with no condition recorded in Fall 2020 (see e-mail from Brett)
  group_by(Type,Species,Distance,Condition_2020fa) %>% 
  summarise(n=n()) %>% 
  mutate(freq = n / sum(n)) %>% # remember one grouping level peeled off with each summarise
  
  ggplot()+
  aes(x=Type,y=freq,fill=Condition_2020fa)+
  geom_bar(stat="identity",position="stack")+
  facet_grid(Species~Distance)+
  xlab("Site type")+
  ylab("Proportion")+
  labs(fill="Seedling condition")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2, hjust=1))


```
\newpage


## Growth
Let's look at leader growth by species, arranged so we can compare seedlot performance between sites.

```{r}



data2020 %>% 
  filter(!Type %in% c("Demo")) %>% # remove frost and demo sites
 
  ggplot()+
  aes(x=Distance,y=Leader,fill=Species)+
  geom_boxplot()+
  facet_grid(Species~Type,scales="free_y")+
  xlab("Seedlot distance")+
  ylab("2020 Leader growth (cm)")+
  labs(fill="Species")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2, hjust=1),
        legend.position = "none")


```

Some of these leader lengths seem exceptionally large.  Notice the Fd with a 60cm leader?  Or many Pli and Lw seedlings with 40cm leaders?  

Also, I am not sure how they measured Cw leaders.  I will follow up with Larry on this.

\newpage

Another way to look at leader growth, arranged so we can compare species performance between sites.

```{r}



data2020 %>% 
  filter(!Type %in% c("Demo")) %>% # remove frost and demo sites
 
  ggplot()+
  aes(x=Distance,y=Leader,fill=Species)+
  geom_boxplot()+
  facet_grid(Type~Species,scales="free_y")+
  xlab("Seedlot distance")+
  ylab("2020 Leader growth (cm)")+
  labs(fill="Species")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2, hjust=1),
        legend.position = "none")


```

Note that the y scale varies between facets.
